Illusion Game Validation (Study 1)

### 2022-08-03 study1.Rmd
move files

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(digits = 3)

@@

# Results

@@

  if(side == "leftright") {
    x <- data[data$Error == 0 & data$Illusion_Side == 1, ]$Answer[1]
    x <- tools::toTitleCase(gsub("arrow", "", x))
    if(x == "Left") data$Answer <- ifelse(data$Illusion_Side == 1, "Left", "Right")
  }

@@

  p1 <- data |> 
    group_by(Illusion_Difference, Illusion_Strength, Answer) |> 
    summarize(Error = mean(Error)) |> 
    mutate(Illusion_Strength = as.factor(Illusion_Strength)) |> 
    ggplot(aes(x = Illusion_Difference, y = Error)) +
    geom_bar(aes(fill=Illusion_Strength), position = position_dodge(width=dodge1), stat="identity") +
    geom_line(aes(color = Illusion_Strength), position = position_dodge(width=dodge1)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_modern() +
    labs(
      color = "Illusion Strength", fill = "Illusion Strength",
      y = "Probability of Error",
      x = "Task Difficulty"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

@@

  p2 <- data |> 
    group_by(Illusion_Difference, Illusion_Strength, Answer) |> 
    summarize(Error = mean(Error)) |> 
    mutate(Illusion_Difference = as.factor(round(Illusion_Difference, 2))) |> 
    ggplot(aes(x = Illusion_Strength, y = Error)) +
    geom_bar(aes(fill=Illusion_Difference), position = position_dodge(width=dodge2), stat="identity") +
    geom_line(aes(color = Illusion_Difference), position = position_dodge(width=dodge2)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_modern() +
    labs(
      color = "Task Difficulty", fill = "Task Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

  if(side == "leftright") {
    p <- ((p1 + facet_wrap(~Answer, ncol=2, labeller = "label_both")) /
      (p2 + facet_wrap(~Answer, ncol=2, labeller = "label_both"))) + 
    plot_annotation(title = "Delboeuf Illusion", 
                    theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
  }
  p
}

@@

```{r message=FALSE, warning=FALSE, cache=cache}
models <- list()
for(i in 1:3) {
  for(j in 1:3) {
    m <- glmmTMB::glmmTMB(
      Error ~ poly(Illusion_Difference, i) * poly(Illusion_Strength, j) + 
        (1 | Participant),
      data = data,
      family = "binomial"
      )
    if(performance::check_convergence(m)) {
      models[[paste0("dif", i, "-str", j)]] <- m
    }
    # m <- glmmTMB::glmmTMB(
    #   Error ~ poly(log(Illusion_Difference), i) * poly(Illusion_Strength, j) + 
    #     (1 | Participant),
    #   data = data,
    #   family = "binomial"
    #   )
    # if(performance::check_convergence(m)) {
    #   models[[paste0("dif(log(", i, "))-str", j)]] <- m
    # }
    m <- glmmTMB::glmmTMB(
      Error ~ Illusion_Side * poly(Illusion_Difference, i) * poly(Illusion_Strength, j) + 
        (1 | Participant),
      data = data,
      family = "binomial"
      )
    if(performance::check_convergence(m)) {
      models[[paste0("side-dif", i, "-str", j)]] <- m
    }
  }
}

test <- test_performance(models, reference=3)
perf <- compare_performance(models, metrics = c("BIC", "R2"))

merge(perf, test) |> 
  arrange(BIC) |> 
  select(Name, BIC, R2_marginal, BF) |> 
  mutate(BF = insight::format_bf(BF, name=""))
```

### Model

@@

@@

  n_lines <- 5
  pred <- estimate_relation(model,
                            at = c("Illusion_Strength", "Illusion_Difference"),
                            length = c(5, n_lines)) |>
    mutate(Illusion_Difference = as.factor(round(Illusion_Difference, 2)))

@@

### Parameter

## Manipulation Checks {.tabset}

### Illusion Side

We tested whether at illusion strength = 0, no effect of right / left (no bias of illusion at 0).

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Error ~ Illusion_Type / Illusion_Side + (1 | Participant),
  data = filter(df, Illusion_Strength == 0),
  family = "binomial"
)

parameters(model, effects = "fixed") |>
  tail(10) |> 
  arrange(p)

# select(filter(df, Error == 0, Illusion_Type == "Müller-Lyer"), Illusion_Side, Answer)
# select(filter(df, Error == 0, Illusion_Type == "Vertical-Horizontal"), Illusion_Side, Answer)
# select(filter(df, Error == 0, Illusion_Type == "Zöllner"), Illusion_Side, Answer)
```

Müller-Lyer: when no illusion, it is easier to answer that the upper line is longer.

### ISI

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Error ~ Illusion_Type / poly(ISI, 2) + (1 | Participant),
  data = df,
  family = "binomial"
)

parameters(model, effects = "fixed") |>
  tail(20)

# select(filter(df, Error == 0, Illusion_Type == "Müller-Lyer"), Illusion_Side, Answer)
# select(filter(df, Error == 0, Illusion_Type == "Vertical-Horizontal"), Illusion_Side, Answer)
# select(filter(df, Error == 0, Illusion_Type == "Zöllner"), Illusion_Side, Answer)
```

## Full Models

### Errors {.tabset}

##### Ebbinghaus

###### Model Selection

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Delboeuf")

models <- list()
for(i in 1:3) {
  for(j in 1:3) {
    m <- glmmTMB::glmmTMB(
      Error ~ poly(Illusion_Difference, i) * poly(Illusion_Strength, j) + 
        (1 | Participant),
      data = data,
      family = "binomial"
      )
    if(performance::check_convergence(m)) {
      models[[paste0("dif", i, "-str", j)]] <- m
    }
    m <- glmmTMB::glmmTMB(
      Error ~ poly(log(Illusion_Difference), i) * poly(Illusion_Strength, j) + 
        (1 | Participant),
      data = data,
      family = "binomial"
      )
    if(performance::check_convergence(m)) {
      models[[paste0("dif(log(", i, "))-str", j)]] <- m
    }
    m <- glmmTMB::glmmTMB(
      Error ~ poly(sqrt(Illusion_Difference), i) * poly(Illusion_Strength, j) + 
        (1 | Participant),
      data = data,
      family = "binomial"
      )
    if(performance::check_convergence(m)) {
      models[[paste0("dif(sqrt(", i, "))-str", j)]] <- m
    }
  }
}

compare_performance(models, metrics = c("BIC", "R2")) |> 
  merge(test_performance(models, reference=6)) |> 
  arrange(BIC) |> 
  select(Name, BIC, R2_marginal, BF) |> 
  mutate(BF = insight::format_bf(BF, name=""))
```

```{r message=FALSE, warning=FALSE}
model_errors <- function(df, illusion = "Delboeuf") {
  data <- filter(df, Illusion_Type == illusion) |>
    mutate(.dots_side = ifelse(Error == 1, "bottom", "top"))

  if (illusion == "Müller-Lyer") {
    formula <- brms::bf(
      # Error ~ t2(Illusion_Difference, Illusion_Strength, k = 4) + (1 | Participant),
      # Error ~ s(Illusion_Strength, by=Illusion_Difference, k = 7) + (1 | Participant),
      Error ~ poly(Illusion_Difference, 3) * poly(Illusion_Strength, 3) * Illusion_Side + 
        (1 | Participant),
      family = "bernoulli"
    )
  } else {
    formula <- brms::bf(
      # Error ~ t2(Illusion_Difference, Illusion_Strength, k = 4) + (1 | Participant),
      # Error ~ s(Illusion_Strength, by=Illusion_Difference, k = 7) + (1 | Participant),
      Error ~ poly(Illusion_Difference, 3) * poly(Illusion_Strength, 3) + 
        (1 | Participant),
      family = "bernoulli"
    )
  }

@@

  # model <- glmmTMB::glmmTMB(
  #   Error ~ Illusion_Difference * Illusion_Strength + (1 | Participant),
  #   data = data,
  #   family = "binomial"
  # )
  # model <- mgcv::gamm(
  #   # Error ~ s(Illusion_Difference, by = Illusion_Strength, k = 4),
  #   Error ~ t2(Illusion_Difference, Illusion_Strength, k = 4),
  #   random = list(Participant = ~1),
  #   data = data,
  #   family = "binomial"
  # )
  # model <- glmmTMB::glmmTMB(
  #   # Error ~ s(Illusion_Difference, by = Illusion_Strength, k = 4),
  #   Error ~ poly(Illusion_Difference, 2) * poly(Illusion_Strength, 2) * Illusion_Side + (1 | Participant),
  #   data = data,
  #   family = "binomial"
  # )

  n_lines <- 5
  pred <- estimate_relation(model,
                            at = c("Illusion_Strength", "Illusion_Difference"),
                            # at = list(Illusion_Strength = unique(data$Illusion_Strength), Illusion_Difference = unique(data$Illusion_Difference)), 
                            length = c(5, n_lines)) |>
    mutate(
      Illusion_Difference = as.factor(Illusion_Difference),
      Illusion_Type = illusion
    )

  p <- pred |>
    ggplot(aes(x = Illusion_Strength, y = Predicted)) +
    geom_dots(
      data = mutate(data, Illusion_Strength = round(Illusion_Strength, 1)),
      aes(x=x, y = Error, group = Error, side = .dots_side), fill = data$color,
      color = NA, alpha=0.5) +
    # geom_dots(
    #   data = mutate(data, Illusion_Strength = round(Illusion_Strength, 1)),
    #   aes(y = Error, group = Error, side = .dots_side),
    #   fill = ifelse(data$Error == 1, "red", "green"), color = NA, alpha=0.2,
    #   position = position_jitter(width=0.05*diff(range(data$Illusion_Strength)), height=0)
    # ) +
    geom_slab(data=data, aes(y = Error)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Illusion_Difference, group = Illusion_Difference), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.05, 0.5, 0.95), linetype = "dotted", alpha = 0.5) +
    geom_line(aes(color = Illusion_Difference, group = Illusion_Difference)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_modern() +
    labs(
      title = paste0(illusion, " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

  list(p = p, model = model, pred = pred)
}
```

## References

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(digits = 3,
        mc.cores = 2)

@@

# Results {.tabset}

@@

  if(side == "leftright") {
    x <- data[data$Error == 0 & data$Illusion_Side == 1, ]$Answer[1]
    x <- tools::toTitleCase(gsub("arrow", "", x))
    if(x == "Left") {
      data$Answer <- ifelse(data$Illusion_Side == 1, "Left", "Right")
    } else {
      data$Answer <- ifelse(data$Illusion_Side == 1, "Right", "Left")
    }
  } else {
    x <- data[data$Error == 0 & data$Illusion_Side == 1, ]$Answer[1]
    x <- tools::toTitleCase(gsub("arrow", "", x))
    if(x == "Up") {
      data$Answer <- ifelse(data$Illusion_Side == 1, "Up", "Down")
    } else {
      data$Answer <- ifelse(data$Illusion_Side == 1, "Down", "Up")
    }
    data$Answer <- fct_rev(data$Answer)
  }

@@

  p1 <- data |> 
    group_by(Illusion_Difference, Illusion_Strength, Answer) |> 
    summarize(Error = mean(Error)) |> 
    mutate(Illusion_Strength = as.factor(round(Illusion_Strength, 2))) |> 
    ggplot(aes(x = Illusion_Difference, y = Error)) +
    geom_bar(aes(fill=Illusion_Strength), position = position_dodge(width=dodge1), stat="identity") +
    geom_line(aes(color = Illusion_Strength), position = position_dodge(width=dodge1)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_modern() +
    labs(
      color = "Illusion Strength", 
      fill = "Illusion Strength",
      y = "Probability of Error",
      x = "Task Difficulty"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

@@

  p2 <- data |> 
    group_by(Illusion_Difference, Illusion_Strength, Answer) |> 
    summarize(Error = mean(Error)) |> 
    mutate(Illusion_Difference = as.factor(round(Illusion_Difference, 2))) |> 
    ggplot(aes(x = Illusion_Strength, y = Error)) +
    geom_vline(xintercept=0, linetype="dotted", alpha=0.6) +
    geom_bar(aes(fill=Illusion_Difference), position = position_dodge(width=dodge2), stat="identity") +
    geom_line(aes(color = Illusion_Difference), position = position_dodge(width=dodge2)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    theme_modern() +
    labs(
      color = "Task Difficulty", 
      fill = "Task Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

  if(side == "leftright") {
    p <- ((p1 + facet_wrap(~Answer, ncol=2, labeller = "label_both")) /
      (p2 + facet_wrap(~Answer, ncol=2, labeller = "label_both"))) + 
    plot_annotation(title = paste(data$Illusion_Type[1], "Illusion"), 
                    theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
  } else {
    p <- ((p1 + facet_wrap(~Answer, nrow=2, labeller = "label_both")) |
      (p2 + facet_wrap(~Answer, nrow=2, labeller = "label_both"))) + 
    plot_annotation(title = paste(data$Illusion_Type[1], "Illusion"), 
                    theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
  }
  p
}

@@

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models <- function(data) {
  models <- list()
  for(i in 1:2) {
    for(j in 1:2) {
      for(k1 in c("", "_log")) {  # c("", "_log")
        for(k2 in c("", "_log")) {  # c("", "_log")
          for(side in c("", "-side")) {
            name <- paste0("dif", k1, i, "-", "str", k2, j, side)
            print(name)
            f <- paste0("poly(Illusion_Difference", 
                        k1,
                        ", ",
                        i,
                        ") * poly(Illusion_Strength",
                        k2, 
                        ", ",
                        j, 
                        ") + (1|Participant)")

            if(side == "-side") f <- paste0("Illusion_Side * ", f)

            m <- glmmTMB::glmmTMB(as.formula(paste0("Error ~ ", f)), 
                                  data = data, family = "binomial")
            if(performance::check_convergence(m)) {
              models[[name]] <- m
            }
          }
        }
      }
    }
  }

  to_keep <- compare_performance(models, metrics = c("BIC")) |> 
    arrange(BIC) |> 
    slice(1:10) |> 
    pull(Name)

  test <- test_performance(models[to_keep], reference=1)
  perf <- compare_performance(models[to_keep], metrics = c("BIC", "R2"))

  merge(perf, test) |> 
    arrange(BIC) |> 
    select(Name, BIC, R2_marginal, BF) |> 
    mutate(BF = insight::format_bf(BF, name=""))
}

best_models(data)
```

### Model Visualization

@@

model <- brms::brm(formula,
  data = data,
  algorithm = "sampling",
  refresh = 200
)
```

@@

  n_lines <- 5
  pred <- estimate_relation(model,
                            at = c("Illusion_Strength", "Illusion_Difference"),
                            length = c(25, n_lines)) |>
    mutate(Illusion_Difference = as.factor(round(Illusion_Difference, 2)))

@@

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
make_gam <- function(data) {

  formula <- brms::bf(
    Error ~ t2(Illusion_Difference, Illusion_Strength, bs = "cr", k=4) + 
      ((1 + Illusion_Difference + Illusion_Strength) | Participant),
    family = "bernoulli"
  )

@@

  list(p = plot_model(data, model), model = model)
}

gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
std_params <- function(model, min=0, max=1) {
  estimate_relation(
  model,
    at = list(Illusion_Strength = c(0), 
              Illusion_Difference = seq(min, max, length.out=500)),
    ) |> 
    select(Illusion_Strength, Illusion_Difference, Error = Predicted) |> 
    slice(c(which.min(abs(Error - 0.005)), 
            which.min(abs(Error - 0.025)), 
            which.min(abs(Error - 0.25)))) |> 
    mutate(Error = insight::format_value(Error, as_percent=TRUE))
}

range(data$Illusion_Difference)
range(data$Illusion_Strength)

std_params(model)
std_params(gam$model)
```

## Ebbinghaus

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Ebbinghaus")

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference * poly(Illusion_Strength, 2) + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)

std_params(model)
std_params(gam$model)
```

## Rod and Frame

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Rod-Frame")

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ poly(Illusion_Difference, 2) * Illusion_Strength + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)
unique(data$Illusion_Strength)

std_params(model, min=0.01, max=12)
std_params(gam$model, min=0.01, max=12)
```

## Vertical-Horizontal

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Vertical-Horizontal")

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference * poly(Illusion_Strength, 2) + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)
unique(data$Illusion_Strength)

std_params(model, min=0, max=0.40)
std_params(gam$model, min=0, max=0.40)
```

## Zöllner

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Zöllner")

plot_descriptive(data)

data <- filter(data, abs(Illusion_Strength) < 45)

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
# model <- glmmTMB::glmmTMB(
#   Error ~ poly(Illusion_Difference, 2) * Illusion_Strength + 
#     ((1 + Illusion_Difference + Illusion_Strength) | Participant),
#   family = "binomial",
#   data=data
# )

formula <- brms::bf(
  Error ~ poly(Illusion_Difference, 2) * Illusion_Strength + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)

std_params(model, min=0, max=5)
```

## White

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "White")

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference * poly(Illusion_Strength, 2) + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)
unique(data$Illusion_Strength)

std_params(model, min=0, max=20)
std_params(gam$model, min=0, max=20)
```

## Ponzo

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Ponzo")

plot_descriptive(data, side = "updown")
```

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference * poly(Illusion_Strength, 2) + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)

std_params(model, min=0, max=20)
std_params(gam$model, min=0, max=20)
```

## Müller-Lyer

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Müller-Lyer")

plot_descriptive(data, side = "updown")
```

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference * poly(Illusion_Strength, 2) + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)

std_params(model, min=0, max=0.6)
std_params(gam$model, min=0, max=0.6)
```

## Poggendorff

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Poggendorff")

plot_descriptive(data, side = "updown")
```

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Side * Illusion_Difference * poly(Illusion_Strength, 2) + 
    ((1 + Illusion_Side + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

parameters::parameters(model)
```

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)

std_params(model, min=0, max=0.5)
std_params(gam$model, min=0, max=0.5)
```

## Contrast

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Contrast")

plot_descriptive(data, side = "updown")
```

```{r message=FALSE, warning=FALSE, cache=cache,results='hide'}
best_models(data)
```

### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  Error ~ Illusion_Difference * poly(Illusion_Strength, 2) + 
    ((1 + Illusion_Difference + Illusion_Strength) | Participant),
  family = "bernoulli"
)

```{r message=FALSE, warning=FALSE, cache=cache}
plot_model(data, model)
```

### GAM

```{r message=FALSE, warning=FALSE, cache=cache}
gam <- make_gam(data)
gam$p
```

### Parameter Standardization

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)

std_params(model, min=0, max=25)
std_params(gam$model, min=0, max=25)
```

## Discussion

This study allowed to elaborate a more precise prior idea regarding the magnitude of the effects at stake and the type of interaction between them. Crucially, it allowed us to refine the range of task difficulty and illusion strength for the stimuli of the next study to maximize the information gain.
